Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
model-based

## Classical strategies: MSY, escapement, total allowable catch

# Reinforcement learning {#sec:DRL}

@@

>>>>

## Classical approaches to sustainable fisheries {#sec:classical}

There are several strategies that have been used to manage fisheries: *escapement*, *maximum sustainable yield (MSY)*, *total allowable catch (TAC)*, among others.
We collectively refere to these as *classical*, and will compare their performance to RL-based management strategies.
As shown in Fig. \ref{fig:tbd}, classical strategies have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $F$). 
A common example is using a logistic growth equation,
$$
  F_{t+1} - F_t = r F_t( 1 - F_t / K),
$$
where the interaction between $F$ and its environment is summarized to two parameters, the growth rate $r$, and the carrying capacity $K$.

# Reinforcement learning {#sec:RL}

@@

## Model-free reinforcement learning

Within control theory, the usual setup is one where we use as much information from the model as possible in order to derive an optimal solution.
**(Wax poetic a bit about Bellmann eq. approaches here?)**

The classical sustainable fishery management approaches summarized in Sec. \ref{sec:classical} are model-based controls.
As we saw in that section, these controls may run into trouble in the case where there are inaccuracies in the model parameter estimates.

More generally, there are many situations in which the exact model of the system is not known or not tractable.
This is a standard situation in ecology: mathematical models capture the most prominent aspects of the ecosystem's dynamics, while ignoring or summarizing most of its complexity.
In this case, it is clear, model-based controls run a grave danger of mismanaging the system.

Reinforcement learning is, on the other hand, typically a model-free approach to control theory.
\footnote{There are, however, approaches to perform model-based reinforcement learning. While we will not focus on these in this paper they are discussed in \cite{tbd1, tbd2}.}
While the model is certainly used to generate training data, it is not directly used by the optimization algorithm.
This provides more flexibility to use model-free RL in instances where the model of the system is not accurately known.
In fact, it has been shown to generally be preferable to use model-free RL in such instances.

**Mention CL here? Where solutions to other related problems in the curriculum are used to build solutions to the target problem.**

This context provides a motivation for this paper. 
Indeed, models for ecosystem dynamics are only ever approximate and incomplete descriptions of reality. 
This way, it is plausible that model-free RL controls outperform currently used model-based controls in ecological management problems.
